---
title: "20230921-misc_adhoc-frames"
author: "Jared Garfinkel"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(gridExtra)
knitr::opts_chunk$set(
	echo = FALSE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

### Purpose

We are counting the number of photos we need to fit our frames. Some frames are single photos, while others are collages. Frames that are collage have more than 1 photo attached. A collage may have 2, 3, 4, or 5 photos each. To better organize our photos, I have created the following tables.

```{r}
df = readxl::read_xlsx("./data/frames.xlsx", sheet= "Sheet1") |> 
  janitor::clean_names() |> 
  mutate(collage_id = na_if(collage_id, "NA"))
```

### Photos

The following is how many photos of each kind there will be. Get more photos than you need in each category so that there are options in each of the 5 sizes. As you can see, there are 34 total pictures required to fit the frames. Since there are 5 sizes, by observation it may make sense to add 5 photos of each size for a set of about 59 prints. Alternatively, doubling the number of photos in each size of frames would be suitable for a set of about 68 prints.

```{r}
df |> 
  group_by(size_in_x_in) |> 
  summarize(number_of_prints = sum(number_of_photos),
            "n+1" = number_of_prints + 1,
            "n+2" = number_of_prints + 2,
            "n+3" = number_of_prints + 3,
            "n+4" = number_of_prints + 4,
            "n+5" = number_of_prints + 5,
            "2n" = number_of_prints * 2) |> 
  janitor::adorn_totals(name = "Totals") |> 
  knitr::kable()
```

### Collages

Since collages can have more than 1 frame attached, some collages have more than 1 size of frame. In other words, multiple sizes of photos may be attached by a collage. To help visualize this, I have included an I.D. variable called "collage_id". This represents the unique collage. As you can see, there are 2 collages with 2 photos, and 1 collage each with 3, 4, and 5 photos. The rest are single photo frames.

```{r}
df |> 
  group_by(collage_id) |> 
  filter(!is.na(collage_id)) |> 
  summarize(number_of_attached_photos = sum(number_of_photos)) |> 
  knitr::kable()
```

Furthermore, it may be desirable to know which size frames fit each collage. As you can see, collage frames 101 and 102 have 2 and 3 size photos, respectively, in a collage. In other words, 2 different size frames are attached by collage frame 101 and 3 different size frames are attached by collage frame 102. For example, frame 101 has 1-3.5 inch x 4 inch and 2-2 inch x 3 inch size photos, while frame 102 has 1-5 inch x 5 inch, 2-2 inch x 3 inch, and 2-3.5 inch x 4 inch photos. Please see below for further details.

```{r}
df |> 
  arrange(collage_id) |> 
  filter(!is.na(collage_id)) |> 
  knitr::kable()
```

### Singles

On ther other hand, some frames only have one picture!

```{r}
df |> 
  filter(is.na(collage_id)) |> 
  arrange(size_in_x_in) |> 
  knitr::kable()
```

### I hope this helps!
